---
title: "NBA Player Data"
execute: 
  echo: true
format:
    html:
        code-fold: true
        toc: false
        mathjax: "local"
filters:
  - webr
webr:
  packages: []
smaller: false
---



```{webr-r}
#| context: setup
#| autorun: true

library(openintro)
library(dplyr)

data(nba_players_19)
players<-nba_players_19[,-4]
colnames(players)<- c("First","Last","Team","Position","Number","Height")
players$Height<-round(players$Height*2.54)
attach(players)
  
```


```{r, include=F}

library(openintro)
library(dplyr)

data(nba_players_19)
players<-nba_players_19[,-4]
players$height<-round(players$height*2.54)
```

The following dataset contains information about the 494 basketball players that played in the NBA during the 2018-2019 season.

- `first_name`: First name.
- `last_name`: Last name.
- `team`: Team the player is on.
- `position`: Player position.
- `number`: Jersey number.
- `height`: Height, in cm.

The data can be found in the following table:

```{r, echo=F}
library(DT)

datatable(players, 
          options = list(pageLength = 15),
          filter  = "bottom") 
```

###

Use the following box to run code to answer your questions about the babyname dataset.


```{webr-r}
#| autorun: false

```












 








