---
title: "Penguins Data"
execute: 
  echo: true
format:
    html:
        code-fold: true
        toc: false
        mathjax: "local"
filters:
  - webr
webr:
  packages: ["palmerpenguins"]
smaller: false
---



```{webr-r}
#| context: setup
#| autorun: true

library(dplyr)
library(palmerpenguins)

penguins <- penguins |> 
  select(species, island, bill_length_mm, flipper_length_mm, body_mass_g, sex) |> na.omit()
  
attach(penguins)
```


```{r, include=F}

library(dplyr)
library(palmerpenguins)

penguins <- penguins |> 
  select(species, island, bill_length_mm, flipper_length_mm, body_mass_g, sex) |> na.omit()
```

This data set contains measurements for penguins found in Antarctica's Palmer Archipelago.

- `species`: Penguin species.
- `island`: Which island the penguin was found on.
- `bill_length_mm`: How long the penguin's bill is (in mm).
- `flipper_length_mm`: How long the penguin's flipper is (in mm).
- `body_mass_g`: How much the penguin weighs (in g).
- `sex`: The sex of the penguin.

The data can be found in the following table:

```{r, echo=F}
library(DT)

datatable(penguins, 
          options = list(pageLength = 15),
          filter = "bottom") 
```

###

Use the following box to run code to answer your questions about the babyname dataset.


```{webr-r}
#| autorun: false

```












 








