---
title: "Pixar Movie Data"
execute: 
  echo: true
format:
    html:
        code-fold: true
        toc: false
        mathjax: "local"
filters:
  - webr
webr:
  packages: ["pixarfilms"]
smaller: false
---



```{webr-r}
#| context: setup
#| autorun: true

library(dplyr)
library(pixarfilms)

pixar<-pixar_films |> 
  full_join(box_office,by="film") |> 
  full_join(public_response,by="film") |> 
  select(film, release_date, run_time, rotten_tomatoes, box_office_worldwide,  budget ) |> 
  na.omit()
  
attach(pixar)
```


```{r, include=F}

library(pixarfilms)
library(dplyr)


pixar<-pixar_films |> 
  full_join(box_office,by="film") |> 
  full_join(public_response,by="film") |> 
  select(film, release_date, run_time, rotten_tomatoes, box_office_worldwide,  budget ) |> 
  na.omit()

```

The data we will be looking at contains information about Pixar films released prior to 2021, as provided by Wikipedia. The following variables were collected for each film:

- `film`: The name of the film.
- `release_date`: The date the film premiered.
- `run_time`: The length of the film in minutes.
- `rotten_tomatoes`: Score from the review-aggregation website Rotten Tomatoes; scored out of 100.
- `box_office_worldwide`: Box office gross amount in U.S. dollars worldwide.
- `budget`: Movie budget in U.S. dollars.

The data can be found in the following table:

```{r, echo=F}
library(DT)

datatable(pixar, 
          options = list(pageLength = 10), filter = "bottom") 
```

###

Use the following box to run code to answer your questions about the pixar dataset.


```{webr-r}
#| autorun: false

```












 








