---
title: "Earthquake Data"
execute: 
  echo: true
format:
    html:
        code-fold: true
        toc: false
        mathjax: "local"
filters:
  - webr
webr:
  packages: []
smaller: false
---



```{webr-r}
#| context: setup
#| autorun: true

library(dplyr)

data(quakes)

attach(quakes)
  
```


```{r, include=F}

library(dplyr)

data(quakes)

```

The following dataset contains the locations of 1000 earthquakes that occurred near Fiji since 1964.

- `lat`: Latitude of the earthquake.
- `long`: Longitude of the earthquake.
- `depth`: Vertical distance (km) of the earthquake from the earth's surface where the fault ruptured.
- `mag`: Richter magnitude of the earthquake.
- `stations`: Number of stations reporting the earthquake.

The data can be found in the following table:

```{r, echo=F}
library(DT)

datatable(quakes, 
          options = list(pageLength = 15),
          filter = "bottom") 
```

###

Use the following box to run code to answer your questions about the babyname dataset.


```{webr-r}
#| autorun: false

```












 








